### 2013-07-02 Tex/chapters/results.tex
Einzelner Tippfehler
Autokorrelation und Fehlerabschätzung aus-/umformuliert

For evaluation the Monte Carlo simulation is run until the system
is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
per site \(E=\frac{1}{N}\hat H\) are calculated and saved for every
\(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
(see also \ref{ssec:eqtime}). The used values for different system sizes
are listed in tab. \ref{tab:tauAndTeq} in numbers of sweeps. Note that
the \(t_{eq}\) values are generously rounded up to be on the safe side
and the \(\tau\) values are determined as the maximum \(\tau\) over all
simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
and rounded up to the next integer.
\begin{table}[htbp]
    \center
    \begin{tabular}{l r r r r r}
        \toprule
        \(L\)    & 16 &  32 &  64 & 128 & 256\\
        \midrule
        \(\tau\) &  3 &   5 &   7 &  12 &  16\\
        \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
        \bottomrule
    \end{tabular}
    \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
    \label{tab:tauAndTeq}
\end{table}\\
In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
the autocorrelation time for \(\sigma=0\) is plotted.
%The \emph{critical slowing down} is visible as a peak.
The plateau at low temperatures is easy to understand considering the
effects of the Wolff algorithm. At low temperatures it flips nearly every
spin in every step, thus the correlation drops to zero after one sweep.
Alternatively the parallel tempering algorithm swaps spin configurations
with possibly different signs, thus having the same effect.
Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
temperature. The cause is probably the effectiveness of the Wolff cluster
algorithm at \(T_c\).
Obviously the autocorrelation time \(\tau\) increases with the system
size. In fact it obeys a power law, which is the expected behaivior of
a dynamical critical exponent \(z\) as mentioned in section \ref{ssec:eqtime}.
In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
over \(L\) and the dynamical exponent \(z'\) is determined as \(z'=0.64(2)\).
This exponent is much higher than the one of Wolff cluster
algorithm at criticality, which is \(z=0.25\)\cite{NewmanBarkema1999}.
So it represents the dynamical exponent for parallel tempering with
Metropolis above criticality and thus is not exactly a critical exponent.
Nevertheless it is interesting, that it obeys a power law just the same.
Anyhow it is a proof for the effectiveness of the Wolff cluster algorithm
at criticality.
    \subfigure[in dependence on the temperature $T$][]
        \label{fig:autocorr:temperatures}
        \includegraphics[width=0.45\textwidth]{plots/autocorrT}
    \subfigure[in dependence on the system size $L$][]
        \label{fig:autocorr:powerLaw}
        \includegraphics[width=0.45\textwidth]{plots/autocorrL}
    \caption[The autocorrelation time $\tau$]
        Dependece of the autocorrelation time $\tau$ on
        \subref{fig:autocorr:temperatures} the temperature $T$ for
            $\sigma=0$ and
        \subref{fig:autocorr:powerLaw} the system size $L$ (errorbars
            are the standard error determined by bootstrapping)
    \label{fig:autocorr}
For every observable \(O\) the expected value \(\avg{O}\) is determined
as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
calculated sweeps totals to
\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
The expected values \(\avg{O}\) for \(100\) different random proximity
graphs with the same disorder parameter \(\sigma\) are then averaged to
\(\overline{\avg{O}}\).
All error bars are estimated by bootstrapping\cite{Bootstrap} with 200
bootstrap samples if not noted otherwise.

@@

        \caption[Critical Temperature over different disorder parameters]
        {
            Top: Mean sum of the coupling constants to all
            neighbors over different disorder parameters for
            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
            Bottom: Critical temperatures normalized by mean sum of the
            coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
            disorder parameters for
            \subref{sfig:Tc_normJ:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc_normJ:GG} the Gabriel Graph.
        }
        \label{fig:TcJ}
    \end{figure}\\
    % I don't know what all that means...
    If on normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
    \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
    jump on the Gabriel graph arises again, but \(T_c\) is now monotonically
    decreasing with increasing disorder parameter \(\sigma\). Moreover
    the forms of both curves are quite similar, but the
    one for the Relative Neighborhood graph \ref{fig:TcJ}\subref{sfig:Tc_norm:RNG}
    is generally lower and spans over a bigger temperature range than
    the curve of the Gabriel graph \ref{fig:TcJ}\subref{sfig:Tc_norm:GG}.
    % Warum??? Die eigenschaften des Graphen sollten mit der Normalisierung erledigt sein.
    % RNG: laengere Kanten -> weniger lokale effekte?
    Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
    disorder has little influence on this normalized critical temperature.
    Also both graph types have a steep decline after the plateau before
    they approach an asymptotic limit for \(\sigma >> 1\)\\\\

>>>>

For evaluation the Monte Carlo simulation is run until the system
is equilibrated after \(t_{eq}\) sweeps. Then the simulation conti <nues
and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
per site \(E=\frac{1}{N}\hat H\) are calculated and saved for every
\(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
(see also \ref{ssec:eqtime}). The used values for different system sizes
are listed in tab. \ref{tab:tauAndTeq} in numbers of sweeps. Note that
the \(t_{eq}\) values are generously rounded up to be on the safe side
and the \(\tau\) values are determined as the maximum \(\tau\) over all
simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
and rounded up to the next integer.
\begin{table}[htbp]
    \center
    \begin{tabular}{l r r r r r}
        \toprule
        \(L\)    & 16 &  32 &  64 & 128 & 256\\
        \midrule
        \(\tau\) &  3 &   5 &   7 &  12 &  16\\
        \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
        \bottomrule
    \end{tabular}
    \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
    \label{tab:tauAndTeq}
\end{table}\\
For every observable \(O\) the expected value \(\avg{O}\) is determined
as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
calculated sweeps totals to
\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
The expected values \(\avg{O}\) for \(100\) different random proximity
graphs with the same disorder parameter \(\sigma\) are then averaged to
\(\overline{\avg{O}}\). Not only the seed to generate the new random
realization of the proximity graph gets changed, but also the seed for
the random numbers used in the Monte Carlo simulation and during the
generation of the random start configuration of the spins.\\
The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrapping
\cite{Bootstrap} with 200 bootstrap samples if not noted otherwise.
Note that while \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
\(\Delta \overline{\avg{O}}\) is not directly, because it is averaged
over different realizations of the random proximity graph, which are
surely uncorrelated.
Because every error mentioned in this thesis is of this type, it is not
necessary to determine \(\tau\) for each observable. Therefore a good
error estimate can be achieved by simple bootstrapping. Though one has
to simulate enough uncorrelated states for each realization, to keep
the \(\Delta \overline{\avg{O}}\) small.

\subsection{Short Analysis of the Autocorrelation Time  $\tau$}
    % Sollte das hier rein?
    Before the results are presented, a short analysis of the
    autocorrelation time \(\tau\) is given, to illustrate the benefits
    of the used Wolff cluster algorithm.\\
    In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
    the autocorrelation time for the magnetization per site \(m\) at \(\sigma=0\) is plotted.
    \begin{figure}[htbp]
        \centering
        \subfigure[in dependence on the temperature $T$][]
        {
            \label{fig:autocorr:temperatures}
            \includegraphics[width=0.45\textwidth]{plots/autocorrT}
        }
        \subfigure[in dependence on the system size $L$][]
        {
            \label{fig:autocorr:powerLaw}
            \includegraphics[width=0.45\textwidth]{plots/autocorrL}
        }
        \caption[The autocorrelation time $\tau$]
        {
            Dependece of the autocorrelation time $\tau$ on
            \subref{fig:autocorr:temperatures} the temperature $T$ for
                $\sigma=0$ and
            \subref{fig:autocorr:powerLaw} the system size $L$ (errorbars
                are the standard error determined by bootstrapping)
        }
        \label{fig:autocorr}
    \end{figure}
    The plateau at low temperatures is easy to understand considering the
    effects of the Wolff algorithm. At low temperatures it flips nearly every
    spin in every step, thus the correlation drops to zero after one sweep.
    Alternatively the parallel tempering algorithm swaps spin configurations
    with possibly different signs, thus having the same effect.
    Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
    temperature. The cause is probably the effectiveness of the Wolff cluster
    algorithm at \(T_c\).
    Obviously the autocorrelation time \(\tau\) increases with the system
    size. In fact it obeys a power law, which is the expected behaivior of
    a dynamical critical exponent \(z\) as mentioned in section \ref{ssec:eqtime}.
    In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
    over \(L\) and the dynamical exponent \(z'\) is determined as \(z'=0.64(2)\).
    This exponent is much higher than the one of Wolff cluster
    algorithm at criticality, which is \(z=0.25\)\cite{NewmanBarkema1999}.
    So it represents the dynamical exponent for parallel tempering with
    Metropolis above criticality and thus is not exactly a critical exponent.
    Nevertheless it is interesting, that it obeys a power law just the same.
    Anyhow it is a proof for the effectiveness of the Wolff cluster algorithm
    at criticality.

@@

        \caption[Critical Temperature over different disorder parameters]
        {
            Top: Mean sum of the coupling constants to all
            neighbors over different disorder parameters for
            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
            Bottom: Critical temperatures normalized by mean sum of the
            coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
            disorder parameters for
            \subref{sfig:Tc_normJ:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc_normJ:GG} the Gabriel Graph.
        }
        \label{fig:TcJ}
    \end{figure}\\
    % I don't know what all that means...
    If one normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
    \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
    jump on the Gabriel graph arises again, but \(T_c\) is now monotonically
    decreasing with increasing disorder parameter \(\sigma\). Moreover
    the forms of both curves are quite similar, but the
    one for the Relative Neighborhood graph \ref{fig:TcJ}\subref{sfig:Tc_norm:RNG}
    is generally lower and spans over a bigger temperature range than
    the curve of the Gabriel graph \ref{fig:TcJ}\subref{sfig:Tc_norm:GG}.
    % Warum??? Die eigenschaften des Graphen sollten mit der Normalisierung erledigt sein.
    % RNG: laengere Kanten -> weniger lokale effekte?
    Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
    disorder has little influence on this normalized critical temperature.
    Also both graph types have a steep decline after the plateau before
    they approach an asymptotic limit for \(\sigma >> 1\)\\\\
